Bias no more! A practical guide to latent mean centering in multilevel models

### 2022-12-07 ms.Rmd
A suggested figure.

>>>>

```{r}
#| label: fig-me-in-means
#| eval: false
#| include: false
#| fig.cap: Illustration of the risks associated with using observed means for group-mean centering, and how those are avoided by using latent means to group-mean center instead.

# A suggestion for an illustrative figure, showing risks (bias) of observed mean centering, but also how latent mean centering avoids them.

tibble(
  n = seq(1, 100, by = .1),
  s = 1/sqrt(n)
  ) %>% 
  ggplot(aes(n, s)) +
  scale_y_continuous(
    "Measurement error in observed mean",
    limits = 0:1, 
    breaks = extended_breaks(),
    expand = expansion(c(.02, .05))
  ) +
  scale_x_continuous(
    "Number of measurements",
    expand = expansion(.025, .025)
  ) +
  # Theoretical measurement error in mean
  geom_line()
  # More lines or panels
  # Observed dynamic panel bias from a simulation
  # geom_line(something something)
  # Observed bias in other covariate from a simulation
  # geom_line(also something something)
  # Latent mean centering results--lines that are not biased
  # geom_line(...)
```
